Eye-tracking

### 2019-02-15 ngrams/prelim_ngrams.Rmd
feathers for childes corpora ngrams

@@

## Zhou
# unigrams
zhou_unigrams <- map(2:10, ~ngram_entropy(zhou_utterances, .x, 1)) %>% 
  bind_rows()

>>>>

shiro_utterances <- get_utterances(corpus = "Shiro") #use gloss

wagner_utterances <- get_utterances(corpus = "Wagner") #use gloss

@@

write_feather(feather(prov_unigrams), here("prov/adult_unigrams.feather"))
## Zhou
# unigrams
zhou_unigrams <- map(2:10, ~ngram_entropy(zhou_utterances, .x, 1)) %>% 
  bind_rows()
